\chapter{Experimental}

\section{Bridge Modifications}

\subsubsection*{3,5-di(\textit{tert}-butyl)-2-nitro-1-bromobenzene \textbf{(1)}}
To a solution of 3,5-di(\textit{tert}-butyl)-bromobenzene (\qty{20.2}{\g}, \qty{75.0}{\mmol}) in glacial acetic acid (\ce{AcOH}, \qty{250}{\ml}) was added \ce{H2SO4} (\qty{100}{\ml}) dropwise over the course of \qty{2}{\hour} (\num{40} drops \unit{\per\minute}) at room temperature. The resulting suspension was subsequently cooled to \qty{0}{\degreeCelsius} while \ce{HNO3} (\qty{4.5}{\ml}) was added. The reaction mixture was stirred at \qty{80}{\degreeCelsius} for \qty{1}{\hour} before it was poured onto ice cold water. The formed precipitate was filtered of, washed with water (2$\times$ \qty{50}{\ml}) and dissolved wet in hot \ce{MeOH}. The solution was left to crystalise at \qty{4}{\degreeCelsius} to give the product as colorless crystals (\qty{18.4}{\g}, \qty{78}{\percent}).

\subsubsection*{2-bromo-4,6-di-\textit{tert}-butylaniline \textbf{(2)}}
A solution of \textbf{1} (\qty{10.5}{\g}, \qty{33.4}{\mmol}) in \ce{$\iPr$OH} (\qty{100}{\ml}) and \ce{AcOH} (\qty{35}{\ml}) was purged with \ce{N2} for \qty{30}{\minute} before \ce{Fe}-powder (\qty{9.4}{\g}, \qty{16.7}{\mmol}, \num{5}\,equiv.) was added and the suspension \ce{N2}-purged for additionaly \qty{10}{\minute}. After the reaction mixture was stirred at room temperature for \qty{48}{\hour}, the solvent was removed under reduced pressure. The resulting precipitate was extracted with \ce{Et2O} (3$\times$\qty{50}{\ml}) and filtered. The organic phase was washed with aq. sat. \ce{NaHCO3} (3$\times$\qty{50}{\ml}), dried with anhydrouse \ce{Na2SO4} and filtered. The solvent was removed under reduced pressure to give the analyticaly pure product as a yellow oil (\qty{9.5}{\g}, quantitative yield).

\subsubsection*{2-bromo-4,6-di-\textit{tert}-butyl-formanilide \textbf{(3)}}
To acetic anhydride (\qty{76}{\ml}) formic acid (\qty{38}{\ml}) was added slowly at \qty{0}{\degreeCelsius} and the solution was purged with \ce{N2} for \qty{20}{\minute} before it was stirred at \qty{50}{\degreeCelsius} for \qty{2}{\hour}. After the reaction mixture was cooled to \qty{0}{\degreeCelsius}, \textbf{2} (\qty{9.5}{\g}, \qty{33.4}{\mmol}) was added and stirred at room temperature for \qty{20}{\minute} before it was poured onto ice cold water (\qty{1}{\l}). The resulting precipitate was filtered of, washed with water and dried under reduced pressure to give the product as a colorless powder (\qty{9.8}{\g}, \qty{94}{\percent}).

