The Born-Oppenheimer approximation is often formulated as follows: With the atomic cores being much heavier then the electrons, the electrons adopt (near) instantly to any change to the core coordinates. While this is a valid interpretation well known as the adiabatic approximation of quantum mechanics, it may not always be helpful as it emphasises a classical viewpoint. The existence of two states (vibronic, for instance) in a transition may be viewed as time dependent; a transition between them a probability in time. This is obviously not true, due to a fundamental quantum mechanical principle, where these states have existed from the beginning. A possibility to circumvent such a (miss-)interpretation would be to view the energetic eigenstates of the core ($T_{N}(\bm{R}) + V_{NN}(\bm{RR})$, where $\bm{R}$ are the core $N$ coordinates) as so much smaller compared to the electronic eigenstates ($T_e(\bm{r}) + V_{ee}(\bm{rr}) + V_{eN}(\bm{rR})$, where $\bm{r}$ are the electron $e$ coordinates) that the interaction between the core movement and the electron movement are not coupled. This opens the way to treat the electronic and core wavefunction independently, where the total is the product of the electronic and core wavefunction $\Psi_{total} = \psi_e\psi_N$. For quantum mechanical calculations, is $\hat{T}_N$ omitted in a first step and added on later on. The Schrödinger equation is now solved as a function (small incrementations) of the core coordinates, hence the reminiscence to adiabatic theorem. 


 states that due to vibrational relaxation being much faster then all other processes subsequent to excitation, luminescence will always only occur from the lowest state of each multiplicity. Depending on whether IC or ISC is the faster process, a chromophore will after VR be in the zero point vibrational state of either a $S_1$ or $T_1$ state. Azulene with its fluorescence from a $S_2$ is one of the few known exceptions to Kasha's rule.

 Teil einer Weltanschauung, die progressiv und positiv daherkommt, aber eigentlich arrogant, banal und weltfremd ist.